SAT Competition 2020\tnoteref{title}

### 2021-01-25 paper/main.tex
took care of some todos

In all tracks it was required to output a model to certify recognising a satisfiable instance.
On the other hand, certificates for unsatisfiable instances (proofs) were required only 
in the Main track (besides the No Limits track).

@@

\todo{on wrong certificate (but still correct result) followed the demotion of the solver to the no-limits track}

@@

\begin{algorithm}[t]
\DontPrintSemicolon

\KwData{$I$ : Set of Instances, $A$ : Set of Authors}
\KwData{Functions $\alpha : I \rightarrow A$ and $\sigma : I \rightarrow \{\mathsf{sat}, \mathsf{unsat}, \mathsf{unknown}\}$}
\KwResult{$S$ : Set of Selected Instances}
\SetKwFunction{rand}{$\mathsf{random}$}
\BlankLine
$S \leftarrow \emptyset$\;

@@

\begin{table}[t]
\small
\centering
\begin{tabular}{llrr}
\bf Family & \bf Author & \bf Submitted & \bf Selected\\
\hline\arrayrulecolor{lightgray}
0/1 Integer Programming & \multirow{4}{*}{Riveros} & 6 & 2 \\
Fermat &  & 8 & 5 \\
Schur Coloring &  & 4 & 2 \\
Sum Subset &  & 5 & 2 \\
\hline
Anti-Bandwidth & Biere & 187 & 14 \\
Baseball Lineup & Hickey & 40 & 13 \\
Bit-Vector & Preiner & 393 & 14 \\
Cellular Automata & Chowdhury & 20 & 12 \\
CNF Miter & Manthey & 38 & 7 \\
Coloring & Oostema & 14 & 14 \\
Core-based Generator & Hartung & 20 & 14 \\
Cover & Gacek & 18 & 13 \\
\hline
\multirow{3}{*}{Cryptography} & Paxian & \multirow{3}{*}{106} & \multirow{3}{*}{34} \\
 & Shaw &  &  \\
 & Soos &  &  \\
\hline
Discrete Logarithm & Jingchao & 20 & 7 \\
Edge Matching & Holten & 58 & 7 \\
Flood-It Puzzle & Stiphout & 40 & 0 \\
HGen & Guanfeng & 20 & 13 \\
Hypertree Decomposition & Schidler & 56 & 14 \\
Influence Maximization & Kochemazov & 20 & 14 \\
Lam Discrete Geometry & Nejati & 20 & 9 \\
Polynomial Multiplication & Maoluo & 20 & 8 \\
Station Repacking & Newman & 20 & 12 \\
Stedman Triples & Johnson & 23 & 7 \\
Tensors & Savicky & 20 & 14 \\
Termination Analysis & Yolcu & 12 & 7 \\
Timetable & Djamegni & 20 & 14 \\
Tournament & Heule & 16 & 14 \\
Vlsat & Bouvier & 36 & 14 \\
\arrayrulecolor{black}
\hline
\multicolumn{2}{r}{$\Sigma$} & 1260 & 300
\end{tabular}
\caption{Families and amounts of newly submitted instances}
\label{tab:families}
\end{table}

@@

\begin{table}[t]
\centering
\begin{tabular}{rcccc}
 & SAT & UNSAT & UNKNOWN & $\Sigma$\\
\hline\arrayrulecolor{lightgray}
New Instances & 114 & 78 & 108 & 300 \\
Old Instances & 21 & 57 & 22 & 100\\
\hline
$\Sigma$ & 135 & 135 & 130 & 400
\end{tabular}
\caption{Amount of old and new instances by result}
\label{tab:final}
\end{table}

@@

Table \ref{tab:planningBenchmarkDist} shows the number of benchmarks generated
by each encoding.

\begin{table}[h]
\centering
\begin{tabular}{llrr}
\multicolumn{2}{l}{Encoding} & SAT& UNSAT\\
\hline\arrayrulecolor{lightgray}
\textbf{H}  & Tree-REX & 15 & 11\\
\textbf{P}  & PASAR & 14 & 14\\
\textbf{ME} & Madagascar $\exists$-step & 5 & 10\\
\textbf{MS} & Madagascar sequential & 66 & 65\\
\hline
&& 100 & 100\\
\end{tabular}
\label{tab:planningBenchmarkDist}
\caption{Number of benchmarks generated by each encoding.}
\end{table}

The benchmarks of the planning track adhere to the naming convention below.
For
% more details and
a complete list of the encoded planning tasks we refer to the
generation script {\color{red}BROKEN LINK}.

${\langle \texttt{SAT/UNSAT} \rangle\_\langle \texttt{encoding} \rangle\_\langle
  \texttt{pathToInstance} \rangle\_\langle \texttt{makespan}
  \rangle\text{.cnf}}$

@@

\begin{table}[ht]
%\smaller
\centering
\begin{tabularx}{\linewidth}{lXc}
\bf Team & \bf Solver & \bf Score\\
\hline
Soos, Cai, Devriendt, Gocht, Shaw, Meel & \solver{CryptoMiniSat 5} & 3 \\
\stack{Biere, Fleury}~ & \solver{CaDiCaL 2020} & 1 \\
Chen & \solver{abcdsat-i20} & 1 \\
Manthey & \solver{Riss 7.1.2} & 1 
\end{tabularx}
\caption[Teams and Solvers in the Incremental Track]{Teams and Solvers in the Incremental Library Track: Score indicates the amount of application categories won with the submission.}
\label{tab:solvers-incremental}
\end{table}

@@

\subsubsection{CryptoMiniSat-CCAnr and CryptoMiniSat5}
\label{sec:cryptominisat}

@@

\subsubsection{Trail Saving and Stable AllUip in CaDiCaL}

@@

\subsubsection{Relaxed Maple newTech}

@@

\begin{table}[b]
%\smaller
\centering
\begin{tabularx}{\linewidth}{Xlccc}
\bf Team & \bf Solver & \bf M & \bf U & \bf S \\
\hline\arrayrulecolor{lightgray}
\multirow{2}{*}{\stack{Vallade, Le Frioux, Baarir, }{Sopena, Kordon}}~
 & \solver{Painless-MCOMSPS-STR-32} & 1 & 2 & 1 \\
 & \solver{Painless-MCOMSPS-STR-64} & 1 & --& --\\
\hline
\multirow{2}{*}{Biere, Fazekas, Heisinger}
 & \solver{Plingeling} & 2 & 1 & 3 \\
 & \solver{Treengeling} & --& --& --\\
\hline
\multirow{2}{*}{Nabeshima, Inoue}
 & \solver{ManyGlucose-32} & 3 & 3 & -- \\
 & \solver{ManyGlucose-64} & -- & 3 & --\\
\hline
\multirow{2}{*}{Tchinda, Djamegni}
 & \solver{painlessmaplevone} & --& --& 2 \\
 & \solver{painlessmaplevtwo} & --& --& 2 \\
\hline
Li, Wu, Xu, Chen & \solver{syrupscavel} & --& --& --\\
%\hline
Chen & \solver{abcdsatptwenty} & --& --& --
\end{tabularx}
\caption{Teams and Solvers participating in the Parallel track.}
\end{table}

\subsubsection{Painless MCOMSPS STR}

\solver{Painless-MCOMSPS-STR} integrates the solver \solver{MapleCOMSPS} in the \solver{Painless} parallelization framework~\cite{Frioux:2017:Painless,Liang:2017:Maplecomsps}. 
The authors submitted a \solver{32 core} and a \solver{64 core} variant and won three awards: first place in the Main track, best score on satisfiable and second best score on unsatisfiable instances. 
The \solver{32 core} variant achieved slightly better scores than the \solver{64 core} variant. 
The \solver{32 core} variant performed much better, such that the runner-up solvers on satisfiable and unsatisfiable instances outperformed the \solver{64 core} variant.

@@

\solver{Painless-MCOMSPS-STR} diversifies mainly via diverse fixed configurations of the branching strategies LRB and VSIDS, and sparse random initialization of variable polarities~\cite{Balyo:2015:HordeSATs}. 
However, a special solver instance performs concurrent clause strengthening~\cite{Wieringa:2013:CCS}. 
Another special solver instance is configured to perform Gaussian elimination during preprocessing. 
\solver{Painless-MCOMSPS-STR} uses an all-to-all strategy for clause sharing with a fixed size clause buffer and an LBD filter with a dynamic limit~\cite{SC2020}.

@@

\solver{Plingeling} achieved the best score on unsatisfiable instances, second place in the Main track, and the third best score on satisfiable instances. 
\solver{Plingeling} is built around the well-known \solver{Lingeling} and did not change since 2016. 
In a global master queue, \solver{Plingeling} shares unit clauses, equivalences and short clauses with a size limit of~$40$ and an LBD limit of~$8$. 
\solver{Plingeling} uses random seeds for diversification via polarities~\cite{Biere:SC2020,Biere:2012:Lingeling}.

@@

\solver{ManyGlucose} was submitted in \solver{32 core} and \solver{64 core} variants. 
The \solver{32 core} variant received two awards in this competition: one third place in the Main track and another third best score on unsatisfiable instances. 
\solver{ManyGlucose} is a fork of \solver{GlucoseSyrup} that uses strategies known from \solver{ManySat} to achieve deterministic solver behaviour~\cite{Audemard:2018:GlucoseSyrup}~\cite{Audemard:2014:LazyClauseExchange}~\cite{Hamadi:2009:ManySat}.

@@

\solver{Painless Maple} received the award for the second best performance in the Sat track but scored last in the Unsat track. 
\solver{Painless Maple} integrates the solver \solver{ExMapleLCMDistChronoBT} into the \solver{Painless} parallelization framework~\cite{Frioux:2017:Painless}.

\solver{Painless Maple} uses a sharing strategy in which the solvers are divided into those which only export clauses and others which import \emph{and} export clauses. 
\solver{Painless Maple} was submitted in two variants \solver{v1} and \solver{v2}. 
\solver{Painless Maple v1} diversifies via hand-crafted heuristic configurations and \solver{Painless Maple v2} diversifies via randomized intialization of branching heuristics~\cite{SC2020}.

@@

\begin{table}[t]
\centering
\begin{tabularx}{\linewidth}{Xlc}
\bf Team & \bf Solver & \bf Rank\\
\hline\arrayrulecolor{lightgray}
Schreiber & \solver{Mallob Mono} & 1\\
Ehlers, Kulczynski, Nowotka, Sieweck & \solver{TopoSAT 2} & 2\\
Riveros & \solver{Slime} & 3\\
\hline
\multirow{2}{*}{Biere, Fazekas, Fleury, Heisinger} & \solver{Paracooba}, & --\\
& \solver{Paracooba-March} & --\\
\hline
Hartung & \solver{CTSat} & --
\end{tabularx}
\caption{Teams and solvers participating in the Cloud track.}
\end{table}

@@

\solver{Mallob} is a fork of the generic massively parallel SAT solver \solver{HordeSAT}~\cite{Balyo:2015:HordeSATs}. 
\solver{Mallob} performs dynamic load balancing through \emph{malleable job scheduling} in case the input contains several SAT instances of varying priorty. 
This functionality is disabled in the submitted variant \solver{Mallob Mono}.

\solver{Mallob} mainly uses \solver{Lingeling-bcj} and diversifies via randomized sparse initialization of branching scores. 
However, as every 14th solver \solver{Mallob} spawns the SLS solver \solver{YalSAT}~\cite{Biere:2018:LingelingYalsat}.

\solver{Mallob} shares clauses by organizing solvers in a binary tree in which clauses are asynchronously aggregated in a buffer which is passed along this tree from leafs to the root. 
Each node performs a three-way merge of its local export buffer and the two incoming buffers. 
The aggregate that approaches the root of the binary tree is then broadcast to all solvers~\cite{Schreiber:SC2020}.

\solver{Mallob} uses a global clause size limit and a dynamic limit for the sharing buffer, which depends on the position in the binary tree and grows while getting closer to the root. 
Clauses are sorted by their size during aggregation, such that smaller clauses are preferred over longer clauses. 
Duplicates are avoided by using a bloom filter which is cleared periodically~\cite{Schreiber:SC2020}.

@@

\solver{TopoSAT~2} is a massively parallel SAT solver using \solver{Glucose~3}~\cite{Audemard:2018:Glucose}~\cite{Ehlers:2018:Toposat2}. 
\solver{TopoSAT~2} uses lock-free clause-exchange for solvers running on the same matching, and Message Passing Interface (MPI) to share clauses between machines~\cite{Hamadi:2009:ManySat}. 
\solver{TopoSAT~2} strengthens clauses before export and delays clause import until the trail-size reaches a local minimum. 
\solver{Toposat~2} diversifies via the strategies used for branching, restarting and clause forgetting~\cite{Ehlers:SC2020}.

@@

\section{More detailed analysis of the Main track results (to be renamed)}

@@

\begin{table}
%\setlength\tabcolsep{1.5pt}
\smaller
%\centering
\begin{tabular}{ccl}
\bf VBS-1 & \bf \% & \bf Solver \\
\hline
46 & 11.5 & \solver{Kissat-unsat} \\
39 & \phantom{0}9.8 & \solver{Kissat-sat} \\
26 & \phantom{0}6.5 & \solver{Kissat} \\
18 & \phantom{0}4.5 & \solver{CMS-ccnr-lsids} \\
14 & \phantom{0}3.5 & \solver{MapleCM+dist+sat2s} \\
13 & \phantom{0}3.2 & \solver{Relaxed} \\
13 & \phantom{0}3.2 & \solver{Maple-alluip-tr.} \\
12 & \phantom{0}3.0 & \solver{upGlucose3.0-PADC} \\
10 & \phantom{0}2.5 & \solver{CMS-ccnr} \\
10 & \phantom{0}2.5 & \solver{CaDiCaL-sc2020} \\
\end{tabular}\qquad%
%~\\[1em]
\begin{tabular}{ccl}
\bf VBS-2 & \bf \% & \bf Solver \\
\hline
131.5 & 32.9 & \solver{Kissat-sat} \\
122.6 & 30.6 & \solver{Kissat} \\
115.4 & 28.9 & \solver{Kissat-unsat} \\
\phantom{0}92.3 & 23.1 & \solver{CMS-ccnr-lsids} \\
\phantom{0}88.8 & 22.2 & \solver{CMS-ccnr} \\
\phantom{0}84.1 & 21.0 & \solver{CaDiCaL-alluip-tr.} \\
\phantom{0}84.0 & 21.0 & \solver{CaDiCaL-alluip} \\
\phantom{0}83.0 & 20.7 & \solver{CaDiCaL-sc2020} \\
\phantom{0}82.3 & 20.6 & \solver{Relaxed-newTech} \\
\phantom{0}81.5 & 20.4 & \solver{Relaxed} \\
\end{tabular}%
~\\[1em]
\begin{tabular}{ccl}
\bf VBS-3 & \bf \% & \bf Solver \\
\hline
13.0 & 3.3 & \solver{Kissat} \\
11.9 & 3.0 & \solver{Kissat-unsat} \\
11.7 & 2.9 & \solver{Relaxed-newTech} \\
11.4 & 2.8 & \solver{Kissat-sat} \\
10.8 & 2.7 & \solver{CaDiCaL-alluip-tr.} \\
10.8 & 2.7 & \solver{CaDiCaL-alluip} \\
10.5 & 2.6 & \solver{Relaxed} \\
10.4 & 2.6 & \solver{CaDiCaL-sc2020} \\
10.3 & 2.6 & \solver{CMS-walksat} \\
\phantom{0}9.6 & 2.4 & \solver{CaDiCaL-trail} \\
\end{tabular}
\caption{VBS metrics for the results of the Main track, all instances. 
The total number of solved problems was 316. 
There were 48 (non-disqualified) solvers (and their configurations).
Each table shows the first ten solvers sorted according to the respective metric.\todo{Maybe move classic PAR-2 ranking also to here for comparison}}
\label{tab:vbsMainALL}
\end{table}

@@

\begin{table}
\centering
\begin{tabularx}{\linewidth}{cXccc}
\bf Iteration & \bf Selected Solver & \bf Solved & \bf Contributes \\ % & covered so far \\
\hline\arrayrulecolor{lightgray}
\phantom{0}1 & \solver{Kissat-sat} & 264 & 264 \\ % & 264 \\
\phantom{0}2 & \solver{CaDiCaL-alluip} & 250 & \phantom{0}22 \\ % & 286 \\
\phantom{0}3 & \solver{f2trc-s} & 214 & \phantom{0}10 \\ % & 296 \\
\phantom{0}4 & \solver{Relaxed-newTech} & 253 & \phantom{00}6 \\ % & 302 \\
\phantom{0}5 & \solver{Kissat-unsat} & 238 & \phantom{00}4 \\ % & 306 \\
\phantom{0}6 & \solver{Relaxed} & 245 & \phantom{00}3 \\ % & 309 \\
\phantom{0}7 & \solver{CMS-walksat} & 243 & \phantom{00}3 \\ % & 312 \\
\phantom{0}8 & \solver{CMS-ccnr-lsids} & 248 & \phantom{00}1 \\ % & 313 \\
\phantom{0}9 & \solver{MapleCBT-DL-v3} & 211 & \phantom{00}1 \\ % & 314 \\
10 & \solver{DurianSat} & 210 & \phantom{00}1 \\ % & 315 \\
11 & \solver{exp-V-LGB-MLD-CBT-DL} & 194 & \phantom{00}1 \\ % & 316 \\
\hline
 & Total & -- & 316 \\
\end{tabularx}
\caption{A greedy set cover of the solved instances by solvers of the Main track.}
\label{tab:gscMain}
\end{table}

@@

One big cluster we can identify are the \emph{Mapel} decedents in the lower left
corner, all of which are modifications of the winners of the SAT Competition
2018 and the SAT Race 2019. \todo{I think... also race vs competition? Sorry I am new
  here NF} The solver \emph{mergesat} does not quite fit into the cluster and
has a comparatively high similarity to the \emph{CryptoMiniSat} (\emph{CMS})
family at the top right. With the exception of \emph{mergesat} and maybe
\emph{DurianSat} we observe a high similarity within the cluster.

@@

\todo{Summarize Winning Strategies}

\todo{Ideas for Future Competitions}

>>>>

In all tracks it was required to output a model to certify recognising a satisfiable instance.
On the other hand, certificates for unsatisfiable instances (proofs) were required only 
in the Main track (besides the No Limits track).
In some cases solvers output the correct result but the repective certificate was wrong. 
Such solvers were demoted to the No-limits track of the competition.

@@

@@

\begin{algorithm}[t]
\DontPrintSemicolon
\small
\KwData{$I$ : Set of Instances, $A$ : Set of Authors}
\KwData{Functions $\alpha : I \rightarrow A$ and $\sigma : I \rightarrow \{\mathsf{sat}, \mathsf{unsat}, \mathsf{unknown}\}$}
\KwResult{$S$ : Set of Selected Instances}
\SetKwFunction{rand}{$\mathsf{random}$}
\BlankLine
$S \leftarrow \emptyset$\;

@@

\begin{table}[t]
\centering\small
\begin{tabular}{llrr}
\bf Family & \bf Author & \bf Submitted & \bf Selected\\
\hline\arrayrulecolor{lightgray}
0/1 Integer Programming & \multirow{4}{*}{Riveros} & 6 & 2 \\
Fermat &  & 8 & 5 \\
Schur Coloring &  & 4 & 2 \\
Sum Subset &  & 5 & 2 \\
\hline
Anti-Bandwidth & Biere & 187 & 14 \\
Baseball Lineup & Hickey & 40 & 13 \\
Bit-Vector & Preiner & 393 & 14 \\
Cellular Automata & Chowdhury & 20 & 12 \\
CNF Miter & Manthey & 38 & 7 \\
Coloring & Oostema & 14 & 14 \\
Core-based Generator & Hartung & 20 & 14 \\
Cover & Gacek & 18 & 13 \\
\hline
\multirow{3}{*}{Cryptography} & Paxian & \multirow{3}{*}{106} & \multirow{3}{*}{34} \\
 & Shaw &  &  \\
 & Soos &  &  \\
\hline
Discrete Logarithm & Jingchao & 20 & 7 \\
Edge Matching & Holten & 58 & 7 \\
Flood-It Puzzle & Stiphout & 40 & 0 \\
HGen & Guanfeng & 20 & 13 \\
Hypertree Decomposition & Schidler & 56 & 14 \\
Influence Maximization & Kochemazov & 20 & 14 \\
Lam Discrete Geometry & Nejati & 20 & 9 \\
Polynomial Multiplication & Maoluo & 20 & 8 \\
Station Repacking & Newman & 20 & 12 \\
Stedman Triples & Johnson & 23 & 7 \\
Tensors & Savicky & 20 & 14 \\
Termination Analysis & Yolcu & 12 & 7 \\
Timetable & Djamegni & 20 & 14 \\
Tournament & Heule & 16 & 14 \\
Vlsat & Bouvier & 36 & 14 \\
\arrayrulecolor{black}
\hline
\multicolumn{2}{r}{$\Sigma$} & 1260 & 300
\end{tabular}
\caption{Families and amounts of newly submitted instances}
\label{tab:families}
\end{table}

@@

\begin{table}[t]
\centering\small
\begin{tabular}{rcccc}
 & SAT & UNSAT & UNKNOWN & $\Sigma$\\
\hline\arrayrulecolor{lightgray}
New Instances & 114 & 78 & 108 & 300 \\
Old Instances & 21 & 57 & 22 & 100\\
\hline
$\Sigma$ & 135 & 135 & 130 & 400
\end{tabular}
\caption{Amount of old and new instances by result}
\label{tab:final}
\end{table}

@@

\begin{table}[t]
\centering\small
\begin{tabular}{llrr}
\multicolumn{2}{l}{Encoding} & SAT& UNSAT\\
\hline\arrayrulecolor{lightgray}
\textbf{H}  & Tree-REX & 15 & 11\\
\textbf{P}  & PASAR & 14 & 14\\
\textbf{ME} & Madagascar $\exists$-step & 5 & 10\\
\textbf{MS} & Madagascar sequential & 66 & 65\\
\hline
&& 100 & 100\\
\end{tabular}
\label{tab:planningBenchmarkDist}
\caption{Number of planning instances generated per encoding.}
\end{table}

Table \ref{tab:planningBenchmarkDist} shows the number of benchmarks generated
by each encoding. 
For a complete list of the encoded planning tasks we refer to the
generation script.\footnote{\url{https://satcompetition.github.io/2020/downloads/SAT2020_planning_generator.tar.xz}} 
The benchmarks of the planning track adhere to the following naming convention:
${\langle \texttt{SAT/UNSAT} \rangle\_\langle \texttt{encoding} \rangle\_\langle
  \texttt{name} \rangle\_\langle \texttt{makespan}
  \rangle\text{.cnf}}$

@@

\begin{table}[ht]
\centering\small
\begin{tabular}{llc}
\bf Team & \bf Solver & \bf Place\\
\hline
Soos, Cai, Devriendt, Gocht, Shaw, Meel & \solver{CryptoMiniSat 5} & 1 \\
Biere, Fleury & \solver{CaDiCaL 2020} & -- \\
Chen & \solver{abcdsat-i20} & -- \\
Manthey & \solver{Riss 7.1.2} & -- 
\end{tabular}
\caption[Teams and Solvers in the Incremental Track]{Teams and Solvers in the Incremental Library Track.}
\label{tab:solvers-incremental}
\end{table}

@@

\subsubsection{CryptoMiniSat}
\label{sec:cryptominisat}

@@

\subsubsection{CaDiCaL AllUip}

@@

\subsubsection{Relaxed newTech}

@@

\begin{table}[b]
\centering\small
\begin{tabular}{llccc}
\bf Team & \bf Solver & \bf U+S & \bf U & \bf S \\
\hline\arrayrulecolor{lightgray}
\multirow{2}{*}{\stack{Vallade, Le Frioux, Baarir, }{Sopena, Kordon}}~
 & \solver{Painless-MCOMSPS-STR-32} & 1 & 2 & 1 \\
 & \solver{Painless-MCOMSPS-STR-64} & 1 & --& --\\
\hline
\multirow{2}{*}{Biere, Fazekas, Heisinger}
 & \solver{Plingeling} & 2 & 1 & 3 \\
 & \solver{Treengeling} & --& --& --\\
\hline
\multirow{2}{*}{Nabeshima, Inoue}
 & \solver{ManyGlucose-32} & 3 & 3 & -- \\
 & \solver{ManyGlucose-64} & -- & 3 & --\\
\hline
\multirow{2}{*}{Tchinda, Djamegni}
 & \solver{Painless-Maple-v1} & --& --& 2 \\
 & \solver{Painless-Maple-v2} & --& --& 2 \\
\hline
Li, Wu, Xu, Chen & \solver{Syrup Scavel} & --& --& --\\
%\hline
Chen & \solver{abcdSAT-p20} & --& --& --
\end{tabular}
\caption{Teams and Solvers participating in the Parallel track.}
\end{table}

\subsubsection{Painless MapleCOMSPS STR}

\solver{Painless-MCOMSPS-STR} integrates the solver \solver{MapleCOMSPS} in the \solver{Painless} parallelization framework~\cite{Frioux:2017:Painless,Liang:2017:Maplecomsps}. 
The authors submitted a \solver{32} and a \solver{64} threaded variant and won three awards: first place overall, best score on satisfiable and second best score on unsatisfiable instances. 
In the overall evaluation, the \solver{32} threaded variant achieved slightly better scores than the \solver{64} threaded variant. 
However, in the separate evaluations on satisfiable and unsatisfiable variants the \solver{32} threaded variants performed much better, such that the runner-up solvers outperformed the \solver{64} threaded variant.

@@

\solver{Painless-MCOMSPS-STR} diversifies mainly via hard-coded configurations of the branching strategies LRB and VSIDS, and via sparse random initialization of variable polarities~\cite{Balyo:2015:HordeSATs}. 
Two special solver instances perform concurrent clause strengthening~\cite{Wieringa:2013:CCS} Gaussian elimination, respectively. 
\solver{Painless-MCOMSPS-STR} uses an all-to-all strategy for clause sharing with a fixed size clause buffer and an LBD filter with a dynamic limit~\cite{SC2020}.

@@

\solver{Plingeling} achieved the best score on unsatisfiable instances, second place in the overall evaluation, and the third best score on satisfiable instances. 
\solver{Plingeling} is built around the well-known \solver{Lingeling} and did not change since 2016. 
In a global master queue, \solver{Plingeling} shares unit clauses, equivalences and short clauses with a size limit of~$40$ and an LBD limit of~$8$. 
\solver{Plingeling} uses random seeds for diversification via variable polarities~\cite{Biere:SC2020,Biere:2012:Lingeling}.

@@

\solver{ManyGlucose} was submitted in \solver{32} and \solver{64} threaded variants. 
The \solver{32} threaded variant received two awards in this competition: the overall third place and third best score on unsatisfiable instances. 
\solver{ManyGlucose} is a fork of \solver{GlucoseSyrup} that uses strategies known from \solver{ManySat} to achieve deterministic solver behaviour~\cite{Audemard:2018:GlucoseSyrup}~\cite{Audemard:2014:LazyClauseExchange}~\cite{Hamadi:2009:ManySat}.

@@

\solver{Painless Maple} received the award for the second best performance on satisfiable instances but had the worst performance on unsatisfiable instances. 
\solver{Painless Maple} integrates the solver \solver{ExMapleLCMDistChronoBT} into the \solver{Painless} parallelization framework~\cite{Frioux:2017:Painless}. 
\solver{Painless Maple} uses a sharing strategy in which the solvers are divided into those which only export clauses and others which import \emph{and} export clauses. 
\solver{Painless Maple} was submitted in two variants \solver{v1} and \solver{v2}. 
\solver{Painless Maple v1} diversifies via hand-crafted heuristic configurations and \solver{Painless Maple v2} diversifies via randomized intialization of branching heuristics~\cite{SC2020}.

@@

\begin{table}[t]
\centering\small
\begin{tabular}{llc}
\bf Team & \bf Solver & \bf Place\\
\hline\arrayrulecolor{lightgray}
Schreiber & \solver{Mallob Mono} & 1\\
Ehlers, Kulczynski, Nowotka, Sieweck & \solver{TopoSAT 2} & 2\\
Riveros & \solver{Slime} & 3\\
\hline
\multirow{2}{*}{Biere, Fazekas, Fleury, Heisinger} & \solver{Paracooba}, & --\\
& \solver{Paracooba-March} & --\\
\hline
Hartung & \solver{CTSat} & --
\end{tabular}
\caption{Teams and solvers participating in the Cloud track.}
\end{table}

@@

\solver{Mallob} is a fork of the generic massively parallel SAT solver \solver{HordeSAT}~\cite{Balyo:2015:HordeSATs}. 
\solver{Mallob} performs dynamic load balancing through \emph{malleable job scheduling} in case the input contains several SAT instances of varying priorty. 
This functionality is disabled in the submitted variant \solver{Mallob Mono}. 
\solver{Mallob} uses \solver{Lingeling-bcj} and as every 14th solver \solver{Mallob} spawns the SLS solver \solver{YalSAT}~\cite{Biere:2018:LingelingYalsat}.
Diversification is done via randomized sparse initialization of branching scores.

\solver{Mallob} shares clauses by organizing solvers in a binary tree in which clauses are asynchronously aggregated in a buffer which is passed along this tree from its leafs to the root. 
Each node performs a three-way merge of its local export buffer and the two incoming buffers. 
The aggregate that approaches the root of the binary tree is then broadcast to all solvers~\cite{Schreiber:SC2020}.

\solver{Mallob} uses a global clause size limit and a dynamic size limit for the sharing buffer, which depends on its position in the binary tree and is larger the closer we get to the root. 
Clauses are sorted by their size during aggregation, such that smaller clauses are preferred over longer clauses. 
Duplicates are avoided by using a bloom filter which is cleared periodically~\cite{Schreiber:SC2020}.

@@

\solver{TopoSAT~2} is a massively parallel SAT solver using \solver{Glucose~3}~\cite{Audemard:2018:Glucose}~\cite{Ehlers:2018:Toposat2}. 
\solver{TopoSAT~2} uses lock-free clause-exchange for solvers on the same machine, and Message Passing Interface (MPI) to share clauses between machines~\cite{Hamadi:2009:ManySat}. 
\solver{TopoSAT~2} strengthens clauses before export and delays clause import until the trail-size reaches a local minimum. 
\solver{Toposat~2} diversifies via strategies used for branching, restarting and clause forgetting~\cite{Ehlers:SC2020}.

@@

\section{Differentiated Analysis of Main Track Results}

@@

\begin{table}
%\setlength\tabcolsep{1.5pt}
\smaller
%\centering
\begin{tabular}{ccl}
\bf VBS-1 & \bf \% & \bf Solver \\
\hline
46 & 11.5 & \solver{Kissat-unsat} \\
39 & \phantom{0}9.8 & \solver{Kissat-sat} \\
26 & \phantom{0}6.5 & \solver{Kissat} \\
18 & \phantom{0}4.5 & \solver{CMS-ccnr-lsids} \\
14 & \phantom{0}3.5 & \solver{MapleCM+dist+sat2s} \\
13 & \phantom{0}3.2 & \solver{Relaxed} \\
13 & \phantom{0}3.2 & \solver{Maple-alluip-tr.} \\
12 & \phantom{0}3.0 & \solver{upGlucose3.0-PADC} \\
10 & \phantom{0}2.5 & \solver{CMS-ccnr} \\
10 & \phantom{0}2.5 & \solver{CaDiCaL-sc2020} \\
\end{tabular}\qquad%
%~\\[1em]
\begin{tabular}{ccl}
\bf VBS-2 & \bf \% & \bf Solver \\
\hline
131.5 & 32.9 & \solver{Kissat-sat} \\
122.6 & 30.6 & \solver{Kissat} \\
115.4 & 28.9 & \solver{Kissat-unsat} \\
\phantom{0}92.3 & 23.1 & \solver{CMS-ccnr-lsids} \\
\phantom{0}88.8 & 22.2 & \solver{CMS-ccnr} \\
\phantom{0}84.1 & 21.0 & \solver{CaDiCaL-alluip-tr.} \\
\phantom{0}84.0 & 21.0 & \solver{CaDiCaL-alluip} \\
\phantom{0}83.0 & 20.7 & \solver{CaDiCaL-sc2020} \\
\phantom{0}82.3 & 20.6 & \solver{Relaxed-newTech} \\
\phantom{0}81.5 & 20.4 & \solver{Relaxed} \\
\end{tabular}%
~\\[1em]
\begin{tabular}{ccl}
\bf VBS-3 & \bf \% & \bf Solver \\
\hline
13.0 & 3.3 & \solver{Kissat} \\
11.9 & 3.0 & \solver{Kissat-unsat} \\
11.7 & 2.9 & \solver{Relaxed-newTech} \\
11.4 & 2.8 & \solver{Kissat-sat} \\
10.8 & 2.7 & \solver{CaDiCaL-alluip-tr.} \\
10.8 & 2.7 & \solver{CaDiCaL-alluip} \\
10.5 & 2.6 & \solver{Relaxed} \\
10.4 & 2.6 & \solver{CaDiCaL-sc2020} \\
10.3 & 2.6 & \solver{CMS-walksat} \\
\phantom{0}9.6 & 2.4 & \solver{CaDiCaL-trail} \\
\end{tabular}
\caption{VBS metrics for the results of the Main track, all instances. 
The total number of solved problems was 316. 
There were 48 (non-disqualified) solvers (and their configurations).
Each table shows the first ten solvers sorted according to the respective metric.}
\label{tab:vbsMainALL}
\end{table}

@@

\begin{table}
\centering\small
\begin{tabularx}{\linewidth}{cXccc}
\bf Iteration & \bf Selected Solver & \bf Solved & \bf Contributes \\ % & covered so far \\
\hline\arrayrulecolor{lightgray}
\phantom{0}1 & \solver{Kissat-sat} & 264 & 264 \\ % & 264 \\
\phantom{0}2 & \solver{CaDiCaL-alluip} & 250 & \phantom{0}22 \\ % & 286 \\
\phantom{0}3 & \solver{f2trc-s} & 214 & \phantom{0}10 \\ % & 296 \\
\phantom{0}4 & \solver{Relaxed-newTech} & 253 & \phantom{00}6 \\ % & 302 \\
\phantom{0}5 & \solver{Kissat-unsat} & 238 & \phantom{00}4 \\ % & 306 \\
\phantom{0}6 & \solver{Relaxed} & 245 & \phantom{00}3 \\ % & 309 \\
\phantom{0}7 & \solver{CMS-walksat} & 243 & \phantom{00}3 \\ % & 312 \\
\phantom{0}8 & \solver{CMS-ccnr-lsids} & 248 & \phantom{00}1 \\ % & 313 \\
\phantom{0}9 & \solver{MapleCBT-DL-v3} & 211 & \phantom{00}1 \\ % & 314 \\
10 & \solver{DurianSat} & 210 & \phantom{00}1 \\ % & 315 \\
11 & \solver{exp-V-LGB-MLD-CBT-DL} & 194 & \phantom{00}1 \\ % & 316 \\
\hline
 & Total & -- & 316 \\
\end{tabularx}
\caption{A greedy set cover of the solved instances by solvers of the Main track.}
\label{tab:gscMain}
\end{table}

@@

One big cluster we can identify are the \emph{Maple} decedents in the lower left
corner, all of which are modifications of the winners of the SAT Competition
2018 and the SAT Race 2019. 
%The solver \emph{mergesat} does not quite fit into the cluster and has a comparatively high similarity to the \emph{CryptoMiniSat} (\emph{CMS}) family at the top right. With the exception of \emph{mergesat} and maybe \emph{DurianSat} we observe a high similarity within the cluster.

@@

All winning solvers of the Main track periodically schedule runs of an SLS solver and import statistical information generated in unsuccessul runs to reconfigure weights in their branching heuristics.

From the results in the Parallel track, we can learn that it is still hard to scale from $32$ to $64$ threads, as in some occassions the $32$ threaded version of the same solver outperformed its $64$ threaded counterpart. 
However, from the winner in the massively parallel Cloud track, we could learn that classic all-to-all clause-sharing can be outperformed by a more sophisticated architecture.
